---
title: "Herbivory analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Exploración de la base de datos

The database on herbivory from six grasshopper species on meadow plants from mid-west France looks as follows:

**NOTE: remember changing the directory when loading the database from a different computer.**

```{r Load and head}
herbivory <- read.table(file = "C:/Users/Granjel RR/Desktop/Nico Gross/Herbivory_2013.txt", header = TRUE, sep = "\t")
head(herbivory)
```
Within this database, the final variable ('Total') represents the sum of the damage of all the plant species in the row.

```{r Summary}
summary(herbivory)
```

## Plot total damage ~ grasshoppers:

I'm plotting now the total damage versus the amount of grasshoppers for each grasshopper species.

```{r Install packages}
# Installing the ggplot2 package for cool graphics and gridExtra for grids
# install.packages("ggplot2")
# install.packages("gridExtra")
```

```{r Cb, fig.height = 8, fig.width = 12}
library(gridExtra)
library(grid)
library(ggplot2)
library(lattice)
Cb_plot <- qplot(x = Cb, y = Total, xlab = "Chorthippus biguttulus (Cb)", ylab = "Total herbivory", data = herbivory)
Cd_plot <- qplot(x = Cd, y = Total, xlab = "Chorthippus dorsatus (Cd)", ylab = " ", data = herbivory)
Ci_plot <- qplot(x = Ci, y = Total, xlab = "Calliptamus italicus (Ci)", ylab = " ", data = herbivory)
Ee_plot <- qplot(x = Ee, y = Total, xlab = "Euchorthippus elegantulus (Ee)", ylab = "Total herbivory", data = herbivory)
Pg_plot <- qplot(x = Pg, y = Total, xlab = "Pezotettix giornae (Pg)", ylab = " ", data = herbivory)
Pp_plot <- qplot(x = Pp, y = Total, xlab = "Pseudochorthippus parallelus (Pp)", ylab = " ", data = herbivory)
herbivory_grasshoppers <- grid.arrange(Cb_plot, Cd_plot, Ci_plot, Ee_plot, Pg_plot, Pp_plot, nrow = 2, ncol = 3)
```

## Trying different models - all the grasshopper species together

Now I'm trying 4 different models and selecting the one that better fits the data (total herbivory ~ all grasshoppers together).

### Linear (a + bx)

```{r Linear model all gh together}
library(nlme)
Grasshoppers_linear <- lme(Total ~ 0 + Cb + Cd + Ci + Ee + Pg + Pp, data = herbivory, random = ~ 1 | block)
summary(Grasshoppers_linear)
```

### Quadratic model (a + x^2)

```{r Quadratic model all gh together}
Grasshoppers_quadratic <- lme(Total ~ 0 + (Cb)^2 + (Cd)^2 + (Ci)^2 + (Ee)^2 + (Pg)^2 + (Pp)^2, data = herbivory, random = ~ 1 | block)
summary(Grasshoppers_quadratic)
```

### Neperian log model (a + log(x+1))

```{r Neperian log model all gh together}
Grasshoppers_log <- lme(Total ~ 0 + log(Cb+1) + log(Cd+1) + log(Ci+1) + log(Ee+1) + log(Pg+1) + log(Pp+1), data = herbivory, random = ~ 1 | block)
summary(Grasshoppers_log)
```

### Exponential model (a + exp(-x))

```{r Exponential model all gh together}
Grasshoppers_exp <- lme(Total ~ 0 + exp(Cb) + exp(Cd) + exp(Ci) + exp(Ee) + exp(Pg) + exp(Pp), data = herbivory, random = ~ 1 | block)
summary(Grasshoppers_exp)
```

## Trying different models - each grasshopper species separately

Now I'm trying the same 4 different models for each grasshopper species separately.

### **Cb (_Chorthippus biguttulus_)**

#### Cb - Linear (a + bx)

```{r Linear model Cb}
Cb_linear <- lme(Total ~ 0 + Cb, data = herbivory, random = ~ 1 | block)
summary(Cb_linear)
```

#### Cb - Quadratic model (a + x^2)

```{r Quadratic model Cb}
Cb_quadratic <- lme(Total ~ 0 + (Cb)^2, data = herbivory, random = ~ 1 | block)
summary(Cb_quadratic)
```

#### Cb - Neperian log model (a + log(x+1))

```{r Neperian log model Cb}
Cb_log <- lme(Total ~ 0 + log(Cb+1), data = herbivory, random = ~ 1 | block)
summary(Cb_log)
```

#### Cb - Exponential model (a + exp(x))

```{r Exponential model Cb}
Cb_exp <- lme(Total ~ 0 + exp(Cb), data = herbivory, random = ~ 1 | block)
summary(Cb_exp)
```

### **Cd (_Chorthippus dorsatus_)**

#### Cd - Linear model (a + bx)

```{r Linear model Cd}
Cd_linear <- lme(Total ~ 0 + Cd, data = herbivory, random = ~ 1 | block)
summary(Cd_linear)
```

#### Cd - Quadratic model (a + x^2)

```{r Quadratic model Cd}
Cd_quadratic <- lme(Total ~ 0 + (Cd)^2, data = herbivory, random = ~ 1 | block)
summary(Cd_quadratic)
```

#### Cd - Neperian log model (a + log(x+1))

```{r Neperian log model Cd}
Cd_log <- lme(Total ~ 0 + log(Cd+1), data = herbivory, random = ~ 1 | block)
summary(Cd_log)
```

#### Cd - Exponential model (a + exp(x))

```{r Exponential model Cd}
Cd_exp <- lme(Total ~ 0 + exp(Cd), data = herbivory, random = ~ 1 | block)
summary(Cd_exp)
```


### **Ci (_Calliptamus italicus_)**

#### Ci - Linear model (a + bx)

```{r Linear model Ci}
Ci_linear <- lme(Total ~ 0 + Ci, data = herbivory, random = ~ 1 | block)
summary(Ci_linear)
```

#### Ci - Quadratic model (a + x^2)

```{r Quadratic model Ci}
Ci_quadratic <- lme(Total ~ 0 + (Ci)^2, data = herbivory, random = ~ 1 | block)
summary(Ci_quadratic)
```

#### Ci - Neperian log model (a + log(x+1))

```{r Neperian log model Ci}
Ci_log <- lme(Total ~ 0 + log(Ci+1), data = herbivory, random = ~ 1 | block)
summary(Ci_log)
```

#### Ci - Exponential model (a + exp(x))

```{r Exponential model Ci}
Ci_exp <- lme(Total ~ 0 + exp(Ci), data = herbivory, random = ~ 1 | block)
summary(Ci_exp)
```

### **Ee (_Euchorthippus elegantulus_)**

#### Ee - Linear model (a + bx)

```{r Linear model Ee}
Ee_linear <- lme(Total ~ 0 + Ee, data = herbivory, random = ~ 1 | block)
summary(Ee_linear)
```

#### Ee - Quadratic model (a + x^2)

```{r Quadratic model Ee}
Ee_quadratic <- lme(Total ~ 0 + (Ee)^2, data = herbivory, random = ~ 1 | block)
summary(Ee_quadratic)
```

#### Ee - Neperian log model (a + log(x+1))

```{r Neperian log model Ee}
Ee_log <- lme(Total ~ 0 + log(Ee+1), data = herbivory, random = ~ 1 | block)
summary(Ee_log)
```

#### Ee - Exponential model (a + exp(x))

```{r Exponential model Ee}
Ee_exp <- lme(Total ~ 0 + exp(Ee), data = herbivory, random = ~ 1 | block)
summary(Ee_exp)
```

### **Pg (_Pezotettix giornae_)**

#### Pg - Linear model (a + bx)

```{r Linear model Pg}
Pg_linear <- lme(Total ~ 0 + Pg, data = herbivory, random = ~ 1 | block)
summary(Pg_linear)
```

#### Pg - Quadratic model (a + x^2)

```{r Quadratic model Pg}
Pg_quadratic <- lme(Total ~ 0 + (Pg)^2, data = herbivory, random = ~ 1 | block)
summary(Pg_quadratic)
```

#### Pg - Neperian log model (a + log(x+1))

```{r Neperian log model Pg}
Pg_log <- lme(Total ~ 0 + log(Pg+1), data = herbivory, random = ~ 1 | block)
summary(Pg_log)
```

#### Pg - Exponential model (a + exp(x))

```{r Exponential model Pg}
Pg_exp <- lme(Total ~ 0 + exp(Pg), data = herbivory, random = ~ 1 | block)
summary(Pg_exp)
```

### **Pp (_Pseudochorthippus parallelus_)**

#### Pp - Linear model (a + bx)

```{r Linear model Pp}
Pp_linear <- lme(Total ~ 0 + Pp, data = herbivory, random = ~ 1 | block)
summary(Pp_linear)
```

#### Pp - Quadratic model (a + x^2)

```{r Quadratic model Pp}
Pp_quadratic <- lme(Total ~ 0 + (Pp)^2, data = herbivory, random = ~ 1 | block)
summary(Pp_quadratic)
```

#### Pp - Neperian log model (a + log(x+1))

```{r Neperian log model Pp}
Pp_log <- lme(Total ~ 0 + log(Pp+1), data = herbivory, random = ~ 1 | block)
summary(Pp_log)
```

#### Pp - Exponential model (a + exp(x))

```{r Exponential model Pp}
Pp_exp <- lme(Total ~ 0 + exp(Pp), data = herbivory, random = ~ 1 | block)
summary(Pp_exp)
```


# PLANTS















