---
title: "Linear models - plants on plants"
author: "Rodrigo R. Granjel"
date: "22nd May 2018"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Loading the database and the packages needed:

```{r install packages}
#install.packages("mgcv")
```

```{r loading database and packages}
library(nlme)
library(mgcv)
French_grasshoppers_dt <- read.table(file = "C:/Users/Granjel RR/Desktop/Nico Gross/French_grasshoppers_dt_modified.txt", header = TRUE, sep = "\t")
#load Oscar directory #French_grasshoppers_dt <- read.table(file ="/Users/oscargodoy/Dropbox/French grasshoppers/French_grasshoppers_dt_modified.txt", header = TRUE, sep = "\t")

## NAs for zeroes
for (i in 1:nrow(French_grasshoppers_dt)){
  for (j in 1:ncol(French_grasshoppers_dt)){
    if (is.na(French_grasshoppers_dt[i,j])){
      French_grasshoppers_dt[i,j] <- 0
    }
  }
}
rm(i, j)
```


# BROERE

```{r BROERE data}
BRO_ERE <- French_grasshoppers_dt
data_BROERE <- French_grasshoppers_dt

for (i in 1:630){
  if ((BRO_ERE$d_BROERE[i] == 0) && (BRO_ERE$d_BROERE[(i+630)] == 0) &&
      (BRO_ERE$d_BROERE[(i+(2*630))] == 0) && (BRO_ERE$d_BROERE[(i+(3*630))] == 0) &&
      (BRO_ERE$d_BROERE[(i+(4*630))] == 0)){
    data_BROERE <- data_BROERE[-c(i, i+630, i+(2*630), i+(3*630), i+(4*630)),]
    ### removing all the datapoint for this plant species
  } else {
    ### no change, all the rows must prevail
  }
}
rm(i, BRO_ERE)
```

```{r BROERE lme}

broere_lme <- lme(d_BROERE ~ BROERE + ARRELA + DACGLO + DAUCAR + PLALAN + POAANG + RANACR + GALVER +
              TRIPRA + SALPRA + CONARV + MEDARA + GERDIS + FESRUB + TRIFLA + ERYNGE + LEUVUL +
              TAROFF + ONOREP + PICECH + CENJAC + ELYREP + ACHMIL + CREPIS + POAPRA + POATRI +
              RUMACE + SONCHU + PICHIE + FESARU + ANTODO + VERBOF + VERPER + GERROT + LOTCOR + Cb
              +Cd + Ci + Ee+ Pg + Pp,
            data = data_BROERE, random =~ 1 | block/treatment/unique, correlation= corAR1(form= ~ d_time|block/treatment/unique), method = "REML")

summary(broere_lme)

#broere_lme <- gamm(d_BROERE ~ s(Cb),data = data_BROERE, random = list(block = ~1), niterPQL=40, correlation= corAR1(form= ~ d_time| unique))
```


# ARRELA

```{r ARRELA data}
ARR_ELA <- French_grasshoppers_dt
data_ARRELA <- French_grasshoppers_dt

for (i in 1:630){
  if ((ARR_ELA$d_ARRELA[i] == 0) && (ARR_ELA$d_ARRELA[(i+630)] == 0) &&
      (ARR_ELA$d_ARRELA[(i+(2*630))] == 0) && (ARR_ELA$d_ARRELA[(i+(3*630))] == 0) &&
      (ARR_ELA$d_ARRELA[(i+(4*630))] == 0)){
    data_ARRELA <- data_ARRELA[-c(i, i+630, i+(2*630), i+(3*630), i+(4*630)),]
    ### removing all the datapoint for this plant species
  } else {
    ### no change, all the rows must prevail
  }
}
rm(i, ARR_ELA)
```

```{r ARRELA lme}
#data_ARRELA2<-data_ARRELA[which(data_ARRELA$d_time<5),] 
#eliminating these times when arrela is growing positively which are times 

  

arrela_lme <- lme(d_ARRELA ~ BROERE + ARRELA + DACGLO + DAUCAR + PLALAN + POAANG + RANACR + GALVER +
              TRIPRA + SALPRA + CONARV + MEDARA + GERDIS + FESRUB + TRIFLA + ERYNGE + LEUVUL +
              TAROFF + ONOREP + PICECH + CENJAC + ELYREP + ACHMIL + CREPIS + POAPRA + POATRI +
              RUMACE + SONCHU + PICHIE + FESARU + ANTODO + VERBOF + VERPER + GERROT + LOTCOR + log(Cb +1)
              + log(Cd+1) + log(Ci+1) + log(Ee+1) + log(Pg+1) + log(Pp+1),
            data = data_ARRELA2, random =~ 1 | block/treatment/unique, correlation= corAR1(form= ~ d_time|block/treatment/unique), method = "REML")
summary(arrela_lme)

```


# DACGLO

```{r DACGLO data}
#creating a dataframe removing the rows when d_DACGLO is NA and changing all the NAs for zeroes
data_DACGLO <- subset(French_grasshoppers_dt, !is.na(d_DACGLO))
for (i in 1:nrow(data_DACGLO)){
  for (j in 1:ncol(data_DACGLO)){
    if (is.na(data_DACGLO[i,j])){
      data_DACGLO[i,j] <- 0
    }
  }
}
rm(i, j)
```

```{r DACGLO lme}
dacglo_lme <- lme(d_DACGLO ~ BROERE + ARRELA + DACGLO + DAUCAR + PLALAN + POAANG + RANACR + GALVER +
              TRIPRA + SALPRA + CONARV + MEDARA + GERDIS + FESRUB + TRIFLA + ERYNGE + LEUVUL +
              TAROFF + ONOREP + PICECH + CENJAC + ELYREP + ACHMIL + CREPIS + POAPRA + POATRI +
              RUMACE + SONCHU + PICHIE + FESARU + ANTODO + VERBOF + VERPER + GERROT + LOTCOR,
            data = data_DACGLO, random = ~ 1 | block, method = "REML")
summary(dacglo_lme)
```

# DAUCAR

```{r DAUCAR data}
#creating a dataframe removing the rows when d_DAUCAR is NA and changing all the NAs for zeroes
data_DAUCAR <- subset(French_grasshoppers_dt, !is.na(d_DAUCAR))
for (i in 1:nrow(data_DAUCAR)){
  for (j in 1:ncol(data_DAUCAR)){
    if (is.na(data_DAUCAR[i,j])){
      data_DAUCAR[i,j] <- 0
    }
  }
}
rm(i, j)
```

```{r DAUCAR lme}
daucar_lme <- lme(d_DAUCAR ~ BROERE + ARRELA + DACGLO + DAUCAR + PLALAN + POAANG + RANACR + GALVER +
              TRIPRA + SALPRA + CONARV + MEDARA + GERDIS + FESRUB + TRIFLA + ERYNGE + LEUVUL +
              TAROFF + ONOREP + PICECH + CENJAC + ELYREP + ACHMIL + CREPIS + POAPRA + POATRI +
              RUMACE + SONCHU + PICHIE + FESARU + ANTODO + VERBOF + VERPER + GERROT + LOTCOR,
            data = data_DAUCAR, random = ~ 1 | block, method = "REML")
summary(daucar_lme)
```


# PLALAN

```{r PLALAN data}
#creating a dataframe removing the rows when d_PLALAN is NA and changing all the NAs for zeroes
data_PLALAN <- subset(French_grasshoppers_dt, !is.na(d_PLALAN))
for (i in 1:nrow(data_PLALAN)){
  for (j in 1:ncol(data_PLALAN)){
    if (is.na(data_PLALAN[i,j])){
      data_PLALAN[i,j] <- 0
    }
  }
}
rm(i, j)
```

```{r PLALAN lme}
plalan_lme <- lme(d_PLALAN ~ BROERE + ARRELA + DACGLO + DAUCAR + PLALAN + POAANG + RANACR + GALVER +
              TRIPRA + SALPRA + CONARV + MEDARA + GERDIS + FESRUB + TRIFLA + ERYNGE + LEUVUL +
              TAROFF + ONOREP + PICECH + CENJAC + ELYREP + ACHMIL + CREPIS + POAPRA + POATRI +
              RUMACE + SONCHU + PICHIE + FESARU + ANTODO + VERBOF + VERPER + GERROT + LOTCOR,
            data = data_PLALAN, random = ~ 1 | block, method = "REML")
summary(plalan_lme)
```


# POAANG

```{r POAANG data}
#creating a dataframe removing the rows when d_POAANG is NA and changing all the NAs for zeroes
data_POAANG <- subset(French_grasshoppers_dt, !is.na(d_POAANG))
for (i in 1:nrow(data_POAANG)){
  for (j in 1:ncol(data_POAANG)){
    if (is.na(data_POAANG[i,j])){
      data_POAANG[i,j] <- 0
    }
  }
}
rm(i, j)
```

```{r POAANG model}
poaang_lme <- lme(d_POAANG ~ BROERE + ARRELA + DACGLO + DAUCAR + PLALAN + POAANG + RANACR + GALVER +
              TRIPRA + SALPRA + CONARV + MEDARA + GERDIS + FESRUB + TRIFLA + ERYNGE + LEUVUL +
              TAROFF + ONOREP + PICECH + CENJAC + ELYREP + ACHMIL + CREPIS + POAPRA + POATRI +
              RUMACE + SONCHU + PICHIE + FESARU + ANTODO + VERBOF + VERPER + GERROT + LOTCOR,
            data = data_POAANG, random = ~ 1 | block, method = "REML")
summary(poaang_lme)
```


# RANACR

```{r RANACR data}
#creating a dataframe removing the rows when d_RANACR is NA and changing all the NAs for zeroes
data_RANACR <- subset(French_grasshoppers_dt, !is.na(d_RANACR))
for (i in 1:nrow(data_RANACR)){
  for (j in 1:ncol(data_RANACR)){
    if (is.na(data_RANACR[i,j])){
      data_RANACR[i,j] <- 0
    }
  }
}
rm(i, j)
```

```{r RANACR lme}
ranacr_lme <- lme(d_RANACR ~ BROERE + ARRELA + DACGLO + DAUCAR + PLALAN + POAANG + RANACR + GALVER +
              TRIPRA + SALPRA + CONARV + MEDARA + GERDIS + FESRUB + TRIFLA + ERYNGE + LEUVUL +
              TAROFF + ONOREP + PICECH + CENJAC + ELYREP + ACHMIL + CREPIS + POAPRA + POATRI +
              RUMACE + SONCHU + PICHIE + FESARU + ANTODO + VERBOF + VERPER + GERROT + LOTCOR,
            data = data_RANACR, random = ~ 1 | block, method = "REML")
summary(ranacr_lme)
```


# GALVER

```{r GALVER data}
#creating a dataframe removing the rows when d_GALVER is NA and changing all the NAs for zeroes
data_GALVER <- subset(French_grasshoppers_dt, !is.na(d_GALVER))
for (i in 1:nrow(data_GALVER)){
  for (j in 1:ncol(data_GALVER)){
    if (is.na(data_GALVER[i,j])){
      data_GALVER[i,j] <- 0
    }
  }
}
rm(i, j)
```

```{r GALVER lme}
galver_lme <- lme(d_GALVER ~ BROERE + ARRELA + DACGLO + DAUCAR + PLALAN + POAANG + RANACR + GALVER +
              TRIPRA + SALPRA + CONARV + MEDARA + GERDIS + FESRUB + TRIFLA + ERYNGE + LEUVUL +
              TAROFF + ONOREP + PICECH + CENJAC + ELYREP + ACHMIL + CREPIS + POAPRA + POATRI +
              RUMACE + SONCHU + PICHIE + FESARU + ANTODO + VERBOF + VERPER + GERROT + LOTCOR,
            data = data_GALVER, random = ~ 1 | block, method = "REML")
summary(galver_lme)
```


# TRIPRA

```{r TRIPRA data}
#creating a dataframe removing the rows when d_TRIPRA is NA and changing all the NAs for zeroes
data_TRIPRA <- subset(French_grasshoppers_dt, !is.na(d_TRIPRA))
for (i in 1:nrow(data_TRIPRA)){
  for (j in 1:ncol(data_TRIPRA)){
    if (is.na(data_TRIPRA[i,j])){
      data_TRIPRA[i,j] <- 0
    }
  }
}
rm(i, j)
```

```{r TRIPRA lme}
tripra_lme <- lme(d_TRIPRA ~ BROERE + ARRELA + DACGLO + DAUCAR + PLALAN + POAANG + RANACR + GALVER +
              TRIPRA + SALPRA + CONARV + MEDARA + GERDIS + FESRUB + TRIFLA + ERYNGE + LEUVUL +
              TAROFF + ONOREP + PICECH + CENJAC + ELYREP + ACHMIL + CREPIS + POAPRA + POATRI +
              RUMACE + SONCHU + PICHIE + FESARU + ANTODO + VERBOF + VERPER + GERROT + LOTCOR,
            data = data_TRIPRA, random = ~ 1 | block, method = "REML")
summary(tripra_lme)
```


#SALPRA

```{r SALPRA data}
#creating a dataframe removing the rows when d_SALPRA is NA and changing all the NAs for zeroes
data_SALPRA <- subset(French_grasshoppers_dt, !is.na(d_SALPRA))
for (i in 1:nrow(data_SALPRA)){
  for (j in 1:ncol(data_SALPRA)){
    if (is.na(data_SALPRA[i,j])){
      data_SALPRA[i,j] <- 0
    }
  }
}
rm(i, j)
```

```{r SALPRA lme}
salpra_lme <- lme(d_SALPRA ~ BROERE + ARRELA + DACGLO + DAUCAR + PLALAN + POAANG + RANACR + GALVER +
              TRIPRA + SALPRA + CONARV + MEDARA + GERDIS + FESRUB + TRIFLA + ERYNGE + LEUVUL +
              TAROFF + ONOREP + PICECH + CENJAC + ELYREP + ACHMIL + CREPIS + POAPRA + POATRI +
              RUMACE + SONCHU + PICHIE + FESARU + ANTODO + VERBOF + VERPER + GERROT + LOTCOR,
            data = data_SALPRA, random = ~ 1 | block, method = "REML")
summary(salpra_lme)
```


#CONARV

```{r CONARV data}
#creating a dataframe removing the rows when d_CONARV is NA and changing all the NAs for zeroes
data_CONARV <- subset(French_grasshoppers_dt, !is.na(d_CONARV))
for (i in 1:nrow(data_CONARV)){
  for (j in 1:ncol(data_CONARV)){
    if (is.na(data_CONARV[i,j])){
      data_CONARV[i,j] <- 0
    }
  }
}
rm(i, j)
```

```{r CONARV lme}
conarv_lme <- lme(d_CONARV ~ BROERE + ARRELA + DACGLO + DAUCAR + PLALAN + POAANG + RANACR + GALVER +
              TRIPRA + SALPRA + CONARV + MEDARA + GERDIS + FESRUB + TRIFLA + ERYNGE + LEUVUL +
              TAROFF + ONOREP + PICECH + CENJAC + ELYREP + ACHMIL + CREPIS + POAPRA + POATRI +
              RUMACE + SONCHU + PICHIE + FESARU + ANTODO + VERBOF + VERPER + GERROT + LOTCOR,
            data = data_CONARV, random = ~ 1 | block, method = "REML")
summary(conarv_lme)
```


#MEDARA

```{r MEDARA data}
#creating a dataframe removing the rows when d_MEDARA is NA and changing all the NAs for zeroes
data_MEDARA <- subset(French_grasshoppers_dt, !is.na(d_MEDARA))
for (i in 1:nrow(data_MEDARA)){
  for (j in 1:ncol(data_MEDARA)){
    if (is.na(data_MEDARA[i,j])){
      data_MEDARA[i,j] <- 0
    }
  }
}
rm(i, j)
```

```{r MEDARA lme}
medara_lme <- lme(d_MEDARA ~ BROERE + ARRELA + DACGLO + DAUCAR + PLALAN + POAANG + RANACR + GALVER +
              TRIPRA + SALPRA + CONARV + MEDARA + GERDIS + FESRUB + TRIFLA + ERYNGE + LEUVUL +
              TAROFF + ONOREP + PICECH + CENJAC + ELYREP + ACHMIL + CREPIS + POAPRA + POATRI +
              RUMACE + SONCHU + PICHIE + FESARU + ANTODO + VERBOF + VERPER + GERROT + LOTCOR,
            data = data_MEDARA, random = ~ 1 | block, method = "REML")
summary(medara_lme)
```


#GERDIS

```{r GERDIS data}
#creating a dataframe removing the rows when d_GERDIS is NA and changing all the NAs for zeroes
data_GERDIS <- subset(French_grasshoppers_dt, !is.na(d_GERDIS))
for (i in 1:nrow(data_GERDIS)){
  for (j in 1:ncol(data_GERDIS)){
    if (is.na(data_GERDIS[i,j])){
      data_GERDIS[i,j] <- 0
    }
  }
}
rm(i, j)
```

```{r GERDIS lme}
gerdis_lme <- lme(d_GERDIS ~ BROERE + ARRELA + DACGLO + DAUCAR + PLALAN + POAANG + RANACR + GALVER +
              TRIPRA + SALPRA + CONARV + MEDARA + GERDIS + FESRUB + TRIFLA + ERYNGE + LEUVUL +
              TAROFF + ONOREP + PICECH + CENJAC + ELYREP + ACHMIL + CREPIS + POAPRA + POATRI +
              RUMACE + SONCHU + PICHIE + FESARU + ANTODO + VERBOF + VERPER + GERROT + LOTCOR,
            data = data_GERDIS, random = ~ 1 | block, method = "REML")
summary(gerdis_lme)
```


#FESRUB

```{r FESRUB data}
#creating a dataframe removing the rows when d_FESRUB is NA and changing all the NAs for zeroes
data_FESRUB <- subset(French_grasshoppers_dt, !is.na(d_FESRUB))
for (i in 1:nrow(data_FESRUB)){
  for (j in 1:ncol(data_FESRUB)){
    if (is.na(data_FESRUB[i,j])){
      data_FESRUB[i,j] <- 0
    }
  }
}
rm(i, j)
```

```{r FESRUB lme}
fesrub_lme <- lme(d_FESRUB ~ BROERE + ARRELA + DACGLO + DAUCAR + PLALAN + POAANG + RANACR + GALVER +
              TRIPRA + SALPRA + CONARV + MEDARA + GERDIS + FESRUB + TRIFLA + ERYNGE + LEUVUL +
              TAROFF + ONOREP + PICECH + CENJAC + ELYREP + ACHMIL + CREPIS + POAPRA + POATRI +
              RUMACE + SONCHU + PICHIE + FESARU + ANTODO + VERBOF + VERPER + GERROT + LOTCOR,
            data = data_FESRUB, random = ~ 1 | block, method = "REML")
summary(fesrub_lme)
```


#TRIFLA

```{r TRIFLA data}
#creating a dataframe removing the rows when d_TRIFLA is NA and changing all the NAs for zeroes
data_TRIFLA <- subset(French_grasshoppers_dt, !is.na(d_TRIFLA))
for (i in 1:nrow(data_TRIFLA)){
  for (j in 1:ncol(data_TRIFLA)){
    if (is.na(data_TRIFLA[i,j])){
      data_TRIFLA[i,j] <- 0
    }
  }
}
rm(i, j)
```

```{r TRIFLA lme}
#trifla_lme <- lme(d_TRIFLA ~ BROERE + ARRELA + DACGLO + DAUCAR + PLALAN + POAANG + RANACR + GALVER +
#              TRIPRA + SALPRA + CONARV + MEDARA + GERDIS + FESRUB + TRIFLA + ERYNGE + LEUVUL +
#              TAROFF + ONOREP + PICECH + CENJAC + ELYREP + ACHMIL + CREPIS + POAPRA + POATRI +
#              RUMACE + SONCHU + PICHIE + FESARU + ANTODO + VERBOF + VERPER + GERROT + LOTCOR,
#            data = data_TRIFLA, random = ~ 1 | block, method = "REML")
#summary(trifla_lme)
```


#ERYNGE

```{r ERYNGE data}
#creating a dataframe removing the rows when d_ERYNGE is NA and changing all the NAs for zeroes
data_ERYNGE <- subset(French_grasshoppers_dt, !is.na(d_ERYNGE))
for (i in 1:nrow(data_ERYNGE)){
  for (j in 1:ncol(data_ERYNGE)){
    if (is.na(data_ERYNGE[i,j])){
      data_ERYNGE[i,j] <- 0
    }
  }
}
rm(i, j)
```

```{r ERYNGE lme}
erynge_lme <- lme(d_ERYNGE ~ BROERE + ARRELA + DACGLO + DAUCAR + PLALAN + POAANG + RANACR + GALVER +
              TRIPRA + SALPRA + CONARV + MEDARA + GERDIS + FESRUB + TRIFLA + ERYNGE + LEUVUL +
              TAROFF + ONOREP + PICECH + CENJAC + ELYREP + ACHMIL + CREPIS + POAPRA + POATRI +
              RUMACE + SONCHU + PICHIE + FESARU + ANTODO + VERBOF + VERPER + GERROT + LOTCOR,
            data = data_ERYNGE, random = ~ 1 | block, method = "REML")
summary(erynge_lme)
```


#LEUVUL

```{r LEUVUL data}
#creating a dataframe removing the rows when d_LEUVUL is NA and changing all the NAs for zeroes
data_LEUVUL <- subset(French_grasshoppers_dt, !is.na(d_LEUVUL))
for (i in 1:nrow(data_LEUVUL)){
  for (j in 1:ncol(data_LEUVUL)){
    if (is.na(data_LEUVUL[i,j])){
      data_LEUVUL[i,j] <- 0
    }
  }
}
rm(i, j)
```

```{r LEUVUL lme}
leuvul_lme <- lme(d_LEUVUL ~ BROERE + ARRELA + DACGLO + DAUCAR + PLALAN + POAANG + RANACR + GALVER +
              TRIPRA + SALPRA + CONARV + MEDARA + GERDIS + FESRUB + TRIFLA + ERYNGE + LEUVUL +
              TAROFF + ONOREP + PICECH + CENJAC + ELYREP + ACHMIL + CREPIS + POAPRA + POATRI +
              RUMACE + SONCHU + PICHIE + FESARU + ANTODO + VERBOF + VERPER + GERROT + LOTCOR,
            data = data_LEUVUL, random = ~ 1 | block, method = "REML")
summary(leuvul_lme)
```


#TAROFF

```{r TAROFF data}
#creating a dataframe removing the rows when d_TAROFF is NA and changing all the NAs for zeroes
data_TAROFF <- subset(French_grasshoppers_dt, !is.na(d_TAROFF))
for (i in 1:nrow(data_TAROFF)){
  for (j in 1:ncol(data_TAROFF)){
    if (is.na(data_TAROFF[i,j])){
      data_TAROFF[i,j] <- 0
    }
  }
}
rm(i, j)
```

```{r TAROFF lme}
taroff_lme <- lme(d_TAROFF ~ BROERE + ARRELA + DACGLO + DAUCAR + PLALAN + POAANG + RANACR + GALVER +
              TRIPRA + SALPRA + CONARV + MEDARA + GERDIS + FESRUB + TRIFLA + ERYNGE + LEUVUL +
              TAROFF + ONOREP + PICECH + CENJAC + ELYREP + ACHMIL + CREPIS + POAPRA + POATRI +
              RUMACE + SONCHU + PICHIE + FESARU + ANTODO + VERBOF + VERPER + GERROT + LOTCOR,
            data = data_TAROFF, random = ~ 1 | block, method = "REML")
summary(taroff_lme)
```


#ONOREP

```{r ONOREP data}
#creating a dataframe removing the rows when d_ONOREP is NA and changing all the NAs for zeroes
data_ONOREP <- subset(French_grasshoppers_dt, !is.na(d_ONOREP))
for (i in 1:nrow(data_ONOREP)){
  for (j in 1:ncol(data_ONOREP)){
    if (is.na(data_ONOREP[i,j])){
      data_ONOREP[i,j] <- 0
    }
  }
}
rm(i, j)
```

```{r ONOREP lme}
#onorep_lme <- lme(d_ONOREP ~ BROERE + ARRELA + DACGLO + DAUCAR + PLALAN + POAANG + RANACR + GALVER +
#              TRIPRA + SALPRA + CONARV + MEDARA + GERDIS + FESRUB + TRIFLA + ERYNGE + LEUVUL +
#              TAROFF + ONOREP + PICECH + CENJAC + ELYREP + ACHMIL + CREPIS + POAPRA + POATRI +
#              RUMACE + SONCHU + PICHIE + FESARU + ANTODO + VERBOF + VERPER + GERROT + LOTCOR,
#            data = data_ONOREP, random = ~ 1 | block, method = "REML")
#summary(onorep_lme)
```


#PICECH

```{r PICECH data}
#creating a dataframe removing the rows when d_PICECH is NA and changing all the NAs for zeroes
data_PICECH <- subset(French_grasshoppers_dt, !is.na(d_PICECH))
for (i in 1:nrow(data_PICECH)){
  for (j in 1:ncol(data_PICECH)){
    if (is.na(data_PICECH[i,j])){
      data_PICECH[i,j] <- 0
    }
  }
}
rm(i, j)
```

```{r PICECH lme}
#picech_lme <- lme(d_PICECH ~ BROERE + ARRELA + DACGLO + DAUCAR + PLALAN + POAANG + RANACR + GALVER +
#              TRIPRA + SALPRA + CONARV + MEDARA + GERDIS + FESRUB + TRIFLA + ERYNGE + LEUVUL +
#              TAROFF + ONOREP + PICECH + CENJAC + ELYREP + ACHMIL + CREPIS + POAPRA + POATRI +
#              RUMACE + SONCHU + PICHIE + FESARU + ANTODO + VERBOF + VERPER + GERROT + LOTCOR,
#            data = data_PICECH, random = ~ 1 | block, method = "REML")
#summary(picech_lme)
```


#CENJAC

```{r CENJAC data}
#creating a dataframe removing the rows when d_CENJAC is NA and changing all the NAs for zeroes
data_CENJAC <- subset(French_grasshoppers_dt, !is.na(d_CENJAC))
for (i in 1:nrow(data_CENJAC)){
  for (j in 1:ncol(data_CENJAC)){
    if (is.na(data_CENJAC[i,j])){
      data_CENJAC[i,j] <- 0
    }
  }
}
rm(i, j)
```

```{r CENJAC lme}
cenjac_lme <- lme(d_CENJAC ~ BROERE + ARRELA + DACGLO + DAUCAR + PLALAN + POAANG + RANACR + GALVER +
              TRIPRA + SALPRA + CONARV + MEDARA + GERDIS + FESRUB + TRIFLA + ERYNGE + LEUVUL +
              TAROFF + ONOREP + PICECH + CENJAC + ELYREP + ACHMIL + CREPIS + POAPRA + POATRI +
              RUMACE + SONCHU + PICHIE + FESARU + ANTODO + VERBOF + VERPER + GERROT + LOTCOR,
            data = data_CENJAC, random = ~ 1 | block, method = "REML")
summary(cenjac_lme)
```


#ELYREP

```{r ELYREP data}
#creating a dataframe removing the rows when d_ELYREP is NA and changing all the NAs for zeroes
data_ELYREP <- subset(French_grasshoppers_dt, !is.na(d_ELYREP))
for (i in 1:nrow(data_ELYREP)){
  for (j in 1:ncol(data_ELYREP)){
    if (is.na(data_ELYREP[i,j])){
      data_ELYREP[i,j] <- 0
    }
  }
}
rm(i, j)
```

```{r ELYREP lme}
#elyrep_lme <- lme(d_ELYREP ~ BROERE + ARRELA + DACGLO + DAUCAR + PLALAN + POAANG + RANACR + GALVER +
#              TRIPRA + SALPRA + CONARV + MEDARA + GERDIS + FESRUB + TRIFLA + ERYNGE + LEUVUL +
#              TAROFF + ONOREP + PICECH + CENJAC + ELYREP + ACHMIL + CREPIS + POAPRA + POATRI +
#              RUMACE + SONCHU + PICHIE + FESARU + ANTODO + VERBOF + VERPER + GERROT + LOTCOR,
#            data = data_ELYREP, random = ~ 1 | block, method = "REML")
#summary(elyrep_lme)
```


#ACHMIL

```{r ACHMIL data}
#creating a dataframe removing the rows when d_ACHMIL is NA and changing all the NAs for zeroes
data_ACHMIL <- subset(French_grasshoppers_dt, !is.na(d_ACHMIL))
for (i in 1:nrow(data_ACHMIL)){
  for (j in 1:ncol(data_ACHMIL)){
    if (is.na(data_ACHMIL[i,j])){
      data_ACHMIL[i,j] <- 0
    }
  }
}
rm(i, j)
```

```{r ACHMIL lme}
#achmil_lme <- lme(d_ACHMIL ~ BROERE + ARRELA + DACGLO + DAUCAR + PLALAN + POAANG + RANACR + GALVER +
#              TRIPRA + SALPRA + CONARV + MEDARA + GERDIS + FESRUB + TRIFLA + ERYNGE + LEUVUL +
#              TAROFF + ONOREP + PICECH + CENJAC + ELYREP + ACHMIL + CREPIS + POAPRA + POATRI +
#              RUMACE + SONCHU + PICHIE + FESARU + ANTODO + VERBOF + VERPER + GERROT + LOTCOR,
#            data = data_ACHMIL, random = ~ 1 | block, method = "REML")
#summary(achmil_lme)
```


#CREPIS

```{r CREPIS data}
#creating a dataframe removing the rows when d_CREPIS is NA and changing all the NAs for zeroes
data_CREPIS <- subset(French_grasshoppers_dt, !is.na(d_CREPIS))
for (i in 1:nrow(data_CREPIS)){
  for (j in 1:ncol(data_CREPIS)){
    if (is.na(data_CREPIS[i,j])){
      data_CREPIS[i,j] <- 0
    }
  }
}
rm(i, j)
```

```{r CREPIS lme}
crepis_lme <- lme(d_CREPIS ~ BROERE + ARRELA + DACGLO + DAUCAR + PLALAN + POAANG + RANACR + GALVER +
              TRIPRA + SALPRA + CONARV + MEDARA + GERDIS + FESRUB + TRIFLA + ERYNGE + LEUVUL +
              TAROFF + ONOREP + PICECH + CENJAC + ELYREP + ACHMIL + CREPIS + POAPRA + POATRI +
              RUMACE + SONCHU + PICHIE + FESARU + ANTODO + VERBOF + VERPER + GERROT + LOTCOR,
            data = data_CREPIS, random = ~ 1 | block, method = "REML")
summary(crepis_lme)
```


#POAPRA

```{r POAPRA data}
#creating a dataframe removing the rows when d_POAPRA is NA and changing all the NAs for zeroes
data_POAPRA <- subset(French_grasshoppers_dt, !is.na(d_POAPRA))
for (i in 1:nrow(data_POAPRA)){
  for (j in 1:ncol(data_POAPRA)){
    if (is.na(data_POAPRA[i,j])){
      data_POAPRA[i,j] <- 0
    }
  }
}
rm(i, j)
```

```{r POAPRA lme}
poapra_lme <- lme(d_POAPRA ~ BROERE + ARRELA + DACGLO + DAUCAR + PLALAN + POAANG + RANACR + GALVER +
              TRIPRA + SALPRA + CONARV + MEDARA + GERDIS + FESRUB + TRIFLA + ERYNGE + LEUVUL +
              TAROFF + ONOREP + PICECH + CENJAC + ELYREP + ACHMIL + CREPIS + POAPRA + POATRI +
              RUMACE + SONCHU + PICHIE + FESARU + ANTODO + VERBOF + VERPER + GERROT + LOTCOR,
            data = data_POAPRA, random = ~ 1 | block, method = "REML")
summary(poapra_lme)
```


#POATRI

```{r POATRI data}
#creating a dataframe removing the rows when d_POATRI is NA and changing all the NAs for zeroes
data_POATRI <- subset(French_grasshoppers_dt, !is.na(d_POATRI))
for (i in 1:nrow(data_POATRI)){
  for (j in 1:ncol(data_POATRI)){
    if (is.na(data_POATRI[i,j])){
      data_POATRI[i,j] <- 0
    }
  }
}
rm(i, j)
```

```{r POATRI lme}
#poatri_lme <- lme(d_POATRI ~ BROERE + ARRELA + DACGLO + DAUCAR + PLALAN + POAANG + RANACR + GALVER +
#              TRIPRA + SALPRA + CONARV + MEDARA + GERDIS + FESRUB + TRIFLA + ERYNGE + LEUVUL +
#              TAROFF + ONOREP + PICECH + CENJAC + ELYREP + ACHMIL + CREPIS + POAPRA + POATRI +
#              RUMACE + SONCHU + PICHIE + FESARU + ANTODO + VERBOF + VERPER + GERROT + LOTCOR,
#            data = data_POATRI, random = ~ 1 | block, method = "REML")
#summary(poatri_lme)
```


#RUMACE

```{r RUMACE data}
#creating a dataframe removing the rows when d_RUMACE is NA and changing all the NAs for zeroes
data_RUMACE <- subset(French_grasshoppers_dt, !is.na(d_RUMACE))
for (i in 1:nrow(data_RUMACE)){
  for (j in 1:ncol(data_RUMACE)){
    if (is.na(data_RUMACE[i,j])){
      data_RUMACE[i,j] <- 0
    }
  }
}
rm(i, j)
```

```{r RUMACE lme}
rumace_lme <- lme(d_RUMACE ~ BROERE + ARRELA + DACGLO + DAUCAR + PLALAN + POAANG + RANACR + GALVER +
              TRIPRA + SALPRA + CONARV + MEDARA + GERDIS + FESRUB + TRIFLA + ERYNGE + LEUVUL +
              TAROFF + ONOREP + PICECH + CENJAC + ELYREP + ACHMIL + CREPIS + POAPRA + POATRI +
              RUMACE + SONCHU + PICHIE + FESARU + ANTODO + VERBOF + VERPER + GERROT + LOTCOR,
            data = data_RUMACE, random = ~ 1 | block, method = "REML")
summary(rumace_lme)
```


#SONCHU

```{r SONCHU data}
#creating a dataframe removing the rows when d_SONCHU is NA and changing all the NAs for zeroes
data_SONCHU <- subset(French_grasshoppers_dt, !is.na(d_SONCHU))
for (i in 1:nrow(data_SONCHU)){
  for (j in 1:ncol(data_SONCHU)){
    if (is.na(data_SONCHU[i,j])){
      data_SONCHU[i,j] <- 0
    }
  }
}
rm(i, j)
```

```{r SONCHU lme}
sonchu_lme <- lme(d_SONCHU ~ BROERE + ARRELA + DACGLO + DAUCAR + PLALAN + POAANG + RANACR + GALVER +
              TRIPRA + SALPRA + CONARV + MEDARA + GERDIS + FESRUB + TRIFLA + ERYNGE + LEUVUL +
              TAROFF + ONOREP + PICECH + CENJAC + ELYREP + ACHMIL + CREPIS + POAPRA + POATRI +
              RUMACE + SONCHU + PICHIE + FESARU + ANTODO + VERBOF + VERPER + GERROT + LOTCOR,
            data = data_SONCHU, random = ~ 1 | block, method = "REML")
summary(sonchu_lme)
```


#### IMPORTANT NOTE:
All the intra-specific coefficients are positive. Does this sound weird? Isn't the intra-specific competition thought to be very dependent on the plant species and, thus, it could be both positive or negative?
Yep, but we are not having something into account - we are not analysing individuals here, we are analysing the cover of a certain species present at a certain spot. I don't see how we can obtain the 'intras' here...








